Review: Crop adaptation through introgression from wild relatives

### 2016-07-11 TiG_prospectus.tex
Li added methods

Second, local ancestry reconvolution (also known as chromosome painting) can identify the genomic regions that come from different source populations \cite{schraiber2015}. 
Such method usually takes phased haplotypes as input and some can even take multiple source populations, such as MULTIMIX \cite{churchhouse2013}.

Third, ABBA-BABA statistics (also known as D-statistics) and its derivatives are widely applied to search for signs of introgression in genomic patterns of shared derived variants between populations or species.

>>>>

Second, local ancestry reconvolution (also known as chromosome painting) can identify the genomic regions that come from different source populations \cite{schraiber2015}. 
Such method usually takes phased haplotypes as input and an exception is MULTIMIX \cite{churchhouse2013}, which can take both phased and unphased haplotypes as input. and unveil the genomic ancestry from multiple source populations.

Third, ABBA-BABA statistics (also known as D-statistics) and its derivatives are widely applied to search for signs of introgression in genomic patterns of shared derived variants between populations or species. 
Based on D-statistics, $\hat{f_{d}}$ \cite{Martin2015} and five-taxon D statistics \cite{pease2015} are developed to localize the genomic regions under introgression. 
The former took allele frequencies from each population/species and the latter detected introgression from the localized phylogenetic pattern. 
Their strength in identifying specific regions enabled us to explore the relationships between introgression and recombination rate / gene density / distribution of deleterious alleles and to better understand the genomic regions penetrable to foreign gene flow.
